---
title: "Assignment 6: ggmaps"
author: "Kayla Ippongi"
output: pdf_document
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(jpeg)
library(png)
library(ggmap)
library(tidyverse)
library(magick)
```

## Regular Bude Map
-map with markers of Bude & North Cornwall Golf Club, Bude Tide Pools, 
The Carrier's Inn Pub and Compass Point lookout
```{r}
#map with bude as center
reg_map <- get_googlemap(center = c("Bude, England"),zoom = 13.5)
location <- data.frame(lat=c(50.82664,50.828579,50.832559,50.828088, 50.832574, 
                             50.830540,50.830066),
                    lon=c(-4.543678,-4.556585,-4.544649,-4.543960, -4.553974, 
                          -4.551349,-4.543023),
                    legend=c("Bude","Compass Point","Bude & North Cornwall Golf Club",
                        "The Carrier's Inn Pub","Bude Tide Pools","Summerleaze Beach",
                        "The Barrel at Bude"))
                           
#path data frame from Carriers Inn Pub and Bude Golf Club
start <- "Bude and North Cornwall Golf Club"
end <- "The Carrier's Inn Pub, The Strand, Bude EX23 8QU, UK"
path <- route(start, end, structure = "route")

ggmap(reg_map)+
  geom_point(data = location, aes(x=lon, y=lat, color = legend), size =3)+
  geom_path(aes(x = lon, y = lat), colour = "blue", size = 1, 
            data = path, lineend = "round"
  )
```


## Water Color Bude Map
-same map with markers of Bude & North Cornwall Golf Club, Bude Tide Pools, 
The Carrier's Inn Pub and Compass Point lookout 

```{r}
#map with bude as center
reg_map <- get_googlemap(center = c("Bude, England"),zoom = 13.5)
location <- data.frame(lat=c(50.82664,50.828579,50.832559,50.828088, 50.832574, 
                             50.830540,50.830066),
                    lon=c(-4.543678,-4.556585,-4.544649,-4.543960, -4.553974, 
                          -4.551349,-4.543023),
                    legend=c("Bude","Compass Point","Bude & North Cornwall Golf Club",
                        "The Carrier's Inn Pub","Bude Tide Pools","Summerleaze Beach",
                        "The Barrel at Bude"))
                           
#path data frame from Carriers Inn Pub and Bude Golf Club
start <- "Bude and North Cornwall Golf Club"
end <- "The Carrier's Inn Pub, The Strand, Bude EX23 8QU, UK"
path <- route(start, end, structure = "route")

watercolor_map <- get_map(location = c("Bude, England"), source="stamen",maptype = "watercolor",zoom = 13)
ggmap(watercolor_map)+  
  geom_point(data = location, aes(x=lon, y=lat, color = legend), size =3)+
  geom_path(aes(x = lon, y = lat), colour = "blue", size = 1, data = path, lineend = "round"
  )
```

## Bude and North Cornwall Golf Club
\includegraphics{img/golf}

## Bude Tide Pools 
\includegraphics{img/tidepools}

## The Carrier's Inn Pub
\includegraphics{img/pub}

## Compass Point 
\includegraphics{img/compasspoint}

##The Summerleaze Beach
\includegraphics[width=400pt,height=350pt]{img/SummerleazeBeach.jpg}

##The Barrel at Bude
\includegraphics[width=400pt,height=350pt]{img/TheBarrelatBude.jpg}